---
title: "Gene Expression Correlation"
author: ""
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Gene Expression Correlation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette reproduces simulations in section 3.2. Gene expression data is stored in `chr1_genes` which contains expression data for 100 genes on chromosome 1 and `dna_rep_gnes` which contains expression data for 100 genes involved in dna replication. Both data sets have 60 individuals.

```{r, echo = FALSE, warning=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(rcc)
```

The simulations shown in section 3.2 are run with a sample size of 30 for both gene sets. The `cor_sim` function generates data and calculates confidence intervals. Data is returned in the same format as `linreg_sim` and `example_sim`.

For the set of genes on chromosome 1:
```{r}
Sigma <- cov(t(chr1_genes))
dim(Sigma)
```
```{r, eval=FALSE}
set.seed(19519)
chr1_sim_results <- cor_sim(Sigma=Sigma, n=30, n.rep=200)
```


For the set of genes involved in DNA replication:
```{r}
Sigma <- cov(t(dna_rep_genes))
dim(Sigma)
```
```{r, eval=FALSE}
set.seed(19500)
dna_rep_sim_results <- cor_sim(Sigma=Sigma, n=30, n.rep=200)
```
